Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-07-27 Manuscript/MPESubmission/Revision/response.tex

"Number of morphological characters ($N_{C}$)" line @@@ %Header in discussion

"Additionally, when both $M_{L}$ reach 50\% missing data and $N_{C}$ reach 50 characters, the matrix does not contain enough phylogenetic information for the fossil taxa to be placed with confidence in the tree (Figure 6)." line @@@

\item{\textcolor{blue}{\textbf{Specific variation of data per fossil:} More importantly, it doesn't seem like missing data varied among fossil taxa, unless I'm misreading. What we really want to know is what happens when some fossil taxa are fragmentary, as this is the most common empirical situation. Thus, there are morphological characters scored for some living taxa, some fossil taxa, and missing from others. It's unclear if this was simulated. It would be good if the authors could detail the case where, say, all living taxa had morphological data (0 Ml), the matrix was large (0 Mc), and Mf varied *among* fossil taxa, such that some fossils had 100\% coverage, and varied down to, say, 5\%. That's the crucial case here.}}

In this study, we applied a similar approach to what the reviewer 2 suggests (i.e. no missing data for living taxa, and maximal number of characters but various amount of missing data for the fossil taxa).
This results are present in figure 4, central row.
However, the amount of changes among the fossil taxa was not set to any specific amount of missing data per fossil (e.g. like the "artificial fossil" approach in Pattinson et al 2014, Syst. Biol.) but we rather treated the missing data in the "whole" fossil record.
Because our fossil taxa and their characters where randomly simulated, we didn't had any \textit{a priori} assumption on how to remove the data.
We therefore decided to randomly remove a certain amount of data among all the fossil.
For example, when removing 75\% of the data for the fossil taxa ($M_F$=75\%) different scenarios could happen, ranging from a "homogeneous" incompleteness data distribution (each specific fossil taxa had 75\% of missing data) to a "heterogeneous" incompleteness data distribution  (80\% of the specific fossil taxa had 5\% available data and 21\% of the specific fossil taxa had 100\% available data).
In empirical matrices, the incompleteness data distribution probably lies in between both models.

Also, a second argument for using this "simplistic" way to deal with the missing data in the fossil record follows our main recommendation from this study: the best way to improve the quality of Total Evidence trees is to have a maximum number of living species with available morphological data.
In fact lines 584 to 589 in the first version of the manuscript (line @@@ in the revised version), we argue that even if the effect of the $M_F$ parameter is important, there is unfortunately not much we can do about it since the completeness of this part of the matrix solely depends on exceptional palaeontological discoveries and excavation effort.
We feel that these parameters, however crucial for our understanding of macroevolution, are unfortunately not predicable and recommendations such as "we need more fossil data" are empty and less practical than "we need more living species data".

### 2015-07-27 Manuscript/MPESubmission/Revision/response.tex

\section{Reviewer 1:}

\begin{enumerate}
\item{\textcolor{blue}{\textbf{Novelty:} The novelty of this study should be spelled out more clearly by more a more thorough review of the literature, not just by referring to a few relevant works, but by pointing out what is so new about this study.
The authors assert that this is the first study to examine the effects of missing morphological data from a total evidence dataset, but that is what Pattinson et al. 2014 did (as well as Wiens 2005).
This study examines it in a different way with a study design that is unique and adds to the field. For example, one feature of this study that is unique is that a tree with fossils is simulated and the data simulated on that tree.
In other studies of missing data, data were removed from living taxa to determine if their positions could still be inferred (Pattinson et al. 2015; Wiens and Tiu 2012).
This study will have bearing on an old assertion that including fossils specifically may help alleviate long-branch attraction, not only additional taxa with varying amounts of missing data, as suggested by others (e.g., Wiens 2005).
Similarly, in the discussion, the authors need to point out how their results fit in with the results of previous research more clearly. }}

\item{\textcolor{blue}{\textbf{Graphical abstract:} Current graphical abstract does not capture the content of the article for readers in a single glance.
The authors should not use red and green together.
Figure 5 illustrates topology distance with different inference methods and varying proportions of missing data in rows vs columns and would make a better graphical abstract.
For the graphical abstract, Fig 5 needs to be made clearer in one glance what is going on.
More details are given in the comments on that figure below.}}

We gladly followed reviewer 1's graphical abstract suggestions and have changed it to be similar to the figure 5. % TG: It's freaking not catchy at all but at this point I give up. I've tried many ways but the flippin' paper IS NOT attractive. It might be useful, well written, interesting, citable, etc... But it won't be sexy.

@@

\item{\textcolor{blue}{\textbf{Highlights:} wording seems awkward}}

We rephrased the highlights of the paper as follows: %3 to 5 bullet points (maximum 85 characters, including spaces, per bullet point). TG: probably need improvement here.

1. The Total Evidence methods allows to combine living and fossil data.
2. This study test the effect of missing morphological data on topology.
3. The number of living taxa with data as the most effect on recovering topology.
4. Bayesian inference outperforms Maximum Likelihood for correct clade recovery.
5. We suggest that the sampling effort should be focused on data for living taxa.

@@

\item{\textcolor{blue}{\textbf{Introduction:} Needs stronger emphasis on what specifically is unique about this study compared to what the many other studies on missing data have done and found.
Clearly outlining the questions in this study that are left open from previous research is important because some of the findings in this study suggest that there may be more error associated with missing data than previous research has suggested.}}

% To do (see reviewer 1 specific comment 13)

\item{\textcolor{blue}{\textbf{Abbreviation:} One suggestion is to consider abbreviating Maximum Likelihood and Bayesian Inference as ML and BI respectively early in the methods and use throughout.}}

We do understand the reviewers concern are agree that ML and BI are two commonly used abbreviations.
Nonetheless, we would rather prefer not abbreviate these terms: in fact, even though they might add some "smoothness" % TG: that's not the word
to the sentences where Maximum Likelihood and/or Bayesian Inference are stated, we think they might add confusion or difficulties to the whole paper.
Spelling out the abbreviation might be locally "heavy" (i.e. in the sentence) but at least are completely clear and does not ask the reader to look back for the actual meaning of such or such abbreviation.
However, we leave this decision to the editor if she judges it better to abbreviate those terms. % TG: or maybe this statement is useless? Of course we leave it to the editor...

@@

\item{\textcolor{blue}{\textbf{Methodology - True tree:} I suggest it warrants comparing at least the 'best' tree to the 'true' tree.}}

We compared both the ``best'' tree and the ``missing-data'' trees to the ``true'' tree as suggested by both reviewer. We did not, however, include the results to the main text (available in appendix @@@).
We justify this decision to both reviewers specific concerns (see reviewer 1 specific comment 25 and reviewer 2 comment 1).

@@

\item{\textcolor{blue}{\textbf{Methodology - Starting tree:} The authors should at least include some analysis in which no starting tree is given, the max. likelihood 'best' tree is given, and / or the 'best' tree is given but with some perturbation.
I fear that one of the main results may be biased due to this one methodological detail - a strong prior on tree topology.
The justification given was 'to speed up the Bayesian analysis' which does not seem adequate, given these datasets are small.}}

We dealt with this legitimate suggestion and ran an extra analysis on a subset of matrices (20 chains and only the trees with the same number of parameters; i.e. $M_L$=0\%, $M_F$=0\% and $M_C$=0\%; $M_L$=10\%, $M_F$=10\% and $M_C$=10\%, etc...) were we reran the Bayesian inference using a random tree rather than the ``true'' tree as a starting tree (default MrBayes procedure).
We found no effect of the starting tree (random or ``true'') on the resulting topology.
We added this analysis to the appendix @@@ and added a short note in the main text.
See details at reviewer 1 specific comment 46 below.

\item{\textcolor{blue}{\textbf{Results - Bhattacharyya meaning:} Some descriptive statistics are given, but it would help to tell us if these differences are meaningful.
For example, on line 414 the Bhattacharrya Coefficients are given suggesting RF distances are lower for ML than BI trees at 0.69, 0.48, and 0.66 - but if this coefficient represents the probability of overlap between distributions then shouldn't the coefficients be $<$0.05 to say that one is lower than the other?
In the table, mean and median values of $<$0.01 and $>$0.85 are highlighted as being the most extreme.
Later the focus on Bhattacharyya Coefficients is 1 when distributions overlap completely and 0 when they do not - should this be the criterion?
Just make it clear early on so the readers knows what to think when they see these numbers. }}

We clarified and unified % TG: or standardised?
the interpretation of the Bhattacharyya Coefficient throughout the manuscript.
We advocate that two distributions are significantly different when their probability of overlapping (the Bhattacharyya Coefficient) is $>$0.05 and that they are significantly similar when this probability is $>$0.95.
Even though other values (e.g. 0.85) are not conclusive, we still reported them to show the relative overlap of the distributions (i.e. two distributions with a coefficient of 0.85 are not significantly similar but are closer to each other than two distributions with a coefficient of 0.15; which are themselves not significantly different but still less closer to each other than the previous ones).
We added the following statement to the main text and to the appendix B:
"When the Bhattacharyya Coefficient between two distributions is $<$0.05, the distributions are significantly different.
When this coefficient is $>$0.95 both distributions are significantly similar.
Values in between these two threshold just show the probability of overlap between the distributions but are not conclusive to assess the similarity or differences between the distributions." line (@@@)

### 2015-07-27 Manuscript/MPESubmission/Revision/OnlineAppendices-LaTeXSuppFiles/AppendixB.tex
Standardised Bhattacharyya coefficient across whole work

>>>>

When the Bhattacharyya Coefficient between two distributions is $<$0.05, the distributions are significantly different.
When this coefficient is $>$0.95 both distributions are significantly similar.
Values in between these two threshold just show the probability of overlap between the distributions but are not conclusive to assess the similarity or differences between the distributions.

### 2015-07-27 Manuscript/MPESubmission/Revision/OnlineAppendices-LaTeXSuppFiles/AppendixC.tex
Standardised Bhattacharyya coefficient across whole work

%Summary of the BC between pairs of methods for the ML parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised metric between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds metric (RF) or the Normalised Triplets metric (Tr) for the $M_{L}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_ML}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.30 & 0.31 & 0.69 & 0.61 & 0.77 & 1.00 \\ 
                                                                       & $Tr$ & 0.79 & 0.81 & 0.84 & 0.86 & 0.85 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.22 & 0.29 & 0.36 & 0.54 & 0.69 \\ 
                                                                       & $Tr$ & 0.08 & 0.42 & 0.53 & 0.51 & 0.74 & 0.78 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.49 & 0.61 & 0.51 & 0.67 & 0.74 \\ 
                                                                       & $Tr$ & 0.21 & 0.61 & 0.70 & 0.63 & 0.81 & 0.81 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.01 & 0.02 & 0.02 & 0.02 & 0.03 & 0.04 \\ 
                                                                       & $Tr$ & 0.08 & 0.69 & 0.78 & 0.64 & 0.79 & 0.84 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.01 & 0.02 & 0.02 & 0.04 & 0.08 & 0.09 \\ 
                                                                       & $Tr$ & 0.21 & 0.74 & 0.75 & 0.68 & 0.84 & 0.87 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.75 & 0.85 & 0.85 & 0.95 & 1.00 \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & 0.96 & 0.95 & 0.97 & 0.98 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MF parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised metric between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds metric (RF) or the Normalised Triplets metric (Tr) for the $M_{F}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_MF}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.00 & 0.25 & 0.48 & 0.50 & 0.76 & 1.00 \\ 
                                                                       & $Tr$ & 0.38 & 0.69 & 0.75 & 0.72 & 0.80 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.18 & 0.32 & 0.36 & 0.47 & 0.77 \\ 
                                                                       & $Tr$ & 0.08 & 0.34 & 0.40 & 0.38 & 0.53 & 0.55 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.47 & 0.71 & 0.60 & 0.86 & 0.94 \\ 
                                                                       & $Tr$ & 0.21 & 0.54 & 0.62 & 0.56 & 0.64 & 0.80 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.00 & 0.00 & 0.01 & 0.01 & 0.01 & 0.03 \\ 
                                                                       & $Tr$ & 0.08 & 0.38 & 0.54 & 0.49 & 0.70 & 0.75 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.00 & 0.02 & 0.02 & 0.02 & 0.04 & 0.04 \\ 
                                                                       & $Tr$ & 0.21 & 0.29 & 0.66 & 0.54 & 0.72 & 0.82 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.69 & 0.72 & 0.71 & 0.72 & 0.72 \\ 
                                                                       & $Tr$ & 0.91 & 0.91 & 0.91 & 0.93 & 0.92 & 0.98 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MC parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised metric between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds metric (RF) or the Normalised Triplets metric (Tr) for the $N_{C}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_MC}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.03 & 0.32 & 0.66 & 0.55 & 0.75 & 1.00 \\ 
                                                                       & $Tr$ & 0.51 & 0.69 & 0.80 & 0.76 & 0.80 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.17 & 0.21 & 0.31 & 0.46 & 0.68 \\ 
                                                                       & $Tr$ & 0.08 & 0.31 & 0.39 & 0.39 & 0.56 & 0.61 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.44 & 0.47 & 0.52 & 0.78 & 0.90 \\ 
                                                                       & $Tr$ & 0.21 & 0.52 & 0.59 & 0.55 & 0.66 & 0.77 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.00 & 0.01 & 0.01 & 0.02 & 0.02 & 0.03 \\ 
                                                                       & $Tr$ & 0.08 & 0.47 & 0.62 & 0.51 & 0.66 & 0.73 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.00 & 0.02 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
                                                                       & $Tr$ & 0.21 & 0.45 & 0.64 & 0.57 & 0.74 & 0.79 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.73 & 0.73 & 0.76 & 0.81 & 0.86 \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & 0.93 & 0.94 & 0.96 & 0.99 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

\begin{table}[ht]
\caption{Summary of the median Bhattacharyya Coefficients comparisons between the missing data parameters. Each value corresponds to the median Bhattacharyya Coefficient between the Normalised metrics (Robinson-Foulds - RF; Triplets - Tr) between the ``best'' and the ``missing data'' trees (as outlined in Figure 2 in the main text) for the the trees with: Missing Living taxa only ($M_L$); Missing Fossil data only ($M_F$); Number of characters only ($N_C$); and the combination of the three parameters (combined).} 
\begin{tabular}{llcccc}  
  \hline
 Method & Metric & $M_L$ & $M_F$ & $N_C$ & combined \\ 
  \hline
Maximum Likelihood & RF & 0.54 & 0.37 & 0.56 & 0.54 \\ 
                   & Tr & 0.80 & 0.75 & 0.80 & 0.79 \\ 
Bayesian consensus & RF & 0.73 & 0.59 & 0.60 & 0.79 \\ 
   & Tr & 0.86 & 0.67 & 0.81 & 0.81 \\ 
Maximum Likelihood bootstraps & RF & 0.98 & 0.96 & 0.97 & 0.78 \\ 
   & Tr & 0.99 & 1.00 & 1.00 & 0.96 \\ 
Bayesian posterior trees & RF & 0.86 & 0.93 & 0.94 & 0.68 \\ 
  & Tr & 0.98 & 0.99 & 0.99 & 0.91 \\ 
 \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Summary of the median Bhattacharyya Coefficients comparisons between the missing data parameters and the methods. Each value corresponds to the median Bhattacharyya Coefficient between the Normalised metrics (Robinson-Foulds - RF; Triplets - Tr) between the `methods (as outlined in Figure 3 in the main text) for the the trees with: Missing Living taxa only ($M_L$); Missing Fossil data only ($M_F$); Number of characters only ($N_C$); and the combination of the three parameters (combined).}
\begin{tabular}{llcccc}  
  \hline
 Method & Metric & $M_L$ & $M_F$ & $N_C$ & combined \\ 
  \hline
Maximum likelihood vs. Bayesian consensus & RF & 0.69 & 0.48 & 0.66 & 0.10 \\ 
   & Tr & 0.84 & 0.75 & 0.80 & 0.61 \\ 
Maximum likelihood vs. Bootstraps & RF & 0.29 & 0.32 & 0.21 & 0.69 \\ 
   & Tr & 0.53 & 0.40 & 0.39 & 0.65 \\ 
Maximum likelihood vs. Bayesian posterior trees & RF & 0.61 & 0.71 & 0.47 & 0.80 \\ 
  & Tr & 0.70 & 0.62 & 0.59 & 0.73 \\ 
Bayesian consensus vs. Bootstraps & RF & 0.02 & 0.01 & 0.01 & 0.00 \\ 
  & Tr & 0.78 & 0.54 & 0.62 & 0.59 \\ 
Bayesian consensus vs. Bayesian posterior trees & RF & 0.02 & 0.02 & 0.04 & 0.01 \\ 
   & Tr & 0.75 & 0.66 & 0.64 & 0.56 \\ 
Boostraps vs. Bayesian posterior trees & RF & 0.85 & 0.72 & 0.73 & 0.85 \\ 
   & Tr & 0.96 & 0.91 & 0.93 & 0.98 \\ 
 \hline
\end{tabular}
\end{table}
%END
\end{document}

>>>>

%Summary of the BC between pairs of methods for the ML parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised metric between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds metric (RF) or the Normalised Triplets metric (Tr) for the $M_{L}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_ML}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.30 & 0.31 & 0.69 & 0.61 & 0.77 & \textbf{1.00} \\ 
                                                                       & $Tr$ & 0.79 & 0.81 & 0.84 & 0.86 & 0.85 & \textbf{1.00} \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & \textbf{0.03} & 0.22 & 0.29 & 0.36 & 0.54 & 0.69 \\ 
                                                                       & $Tr$ & 0.08 & 0.42 & 0.53 & 0.51 & 0.74 & 0.78 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & \textbf{0.02} & 0.49 & 0.61 & 0.51 & 0.67 & 0.74 \\ 
                                                                       & $Tr$ & 0.21 & 0.61 & 0.70 & 0.63 & 0.81 & 0.81 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & \textbf{0.01} & \textbf{0.02} & \textbf{0.02} & \textbf{0.02} & \textbf{0.03} & \textbf{0.04} \\ 
                                                                       & $Tr$ & 0.08 & 0.69 & 0.78 & 0.64 & 0.79 & 0.84 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & \textbf{0.01} & \textbf{0.02} & \textbf{0.02} & \textbf{0.04} & 0.08 & 0.09 \\ 
                                                                       & $Tr$ & 0.21 & 0.74 & 0.75 & 0.68 & 0.84 & 0.87 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.75 & 0.85 & 0.85 & \textbf{0.95} & \textbf{1.00} \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & \textbf{0.96} & \textbf{0.95} & \textbf{0.97} & \textbf{0.98} \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MF parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised metric between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds metric (RF) or the Normalised Triplets metric (Tr) for the $M_{F}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_MF}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & \textbf{0.00} & 0.25 & 0.48 & 0.50 & 0.76 & \textbf{1.00} \\ 
                                                                       & $Tr$ & 0.38 & 0.69 & 0.75 & 0.72 & 0.80 & \textbf{1.00} \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & \textbf{0.03} & 0.18 & 0.32 & 0.36 & 0.47 & 0.77 \\ 
                                                                       & $Tr$ & 0.08 & 0.34 & 0.40 & 0.38 & 0.53 & 0.55 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & \textbf{0.02} & 0.47 & 0.71 & 0.60 & 0.86 & 0.94 \\ 
                                                                       & $Tr$ & 0.21 & 0.54 & 0.62 & 0.56 & 0.64 & 0.80 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & \textbf{0.00} & \textbf{0.00} & \textbf{0.01} & \textbf{0.01} & \textbf{0.01} & \textbf{0.03} \\ 
                                                                       & $Tr$ & 0.08 & 0.38 & 0.54 & 0.49 & 0.70 & 0.75 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & \textbf{0.00} & \textbf{0.02} & \textbf{0.02} & \textbf{0.02} & \textbf{0.04} & \textbf{0.04} \\ 
                                                                       & $Tr$ & 0.21 & 0.29 & 0.66 & 0.54 & 0.72 & 0.82 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.69 & 0.72 & 0.71 & 0.72 & 0.72 \\ 
                                                                       & $Tr$ & 0.91 & 0.91 & 0.91 & 0.93 & 0.92 & \textbf{0.98} \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MC parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised metric between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds metric (RF) or the Normalised Triplets metric (Tr) for the $N_{C}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_MC}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & \textbf{0.03} & 0.32 & 0.66 & 0.55 & 0.75 & \textbf{1.00} \\ 
                                                                       & $Tr$ & 0.51 & 0.69 & 0.80 & 0.76 & 0.80 & \textbf{1.00} \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & \textbf{0.03} & 0.17 & 0.21 & 0.31 & 0.46 & 0.68 \\ 
                                                                       & $Tr$ & 0.08 & 0.31 & 0.39 & 0.39 & 0.56 & 0.61 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & \textbf{0.02} & 0.44 & 0.47 & 0.52 & 0.78 & 0.90 \\ 
                                                                       & $Tr$ & 0.21 & 0.52 & 0.59 & 0.55 & 0.66 & 0.77 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & \textbf{0.00} & \textbf{0.01} & \textbf{0.01} & \textbf{0.02} & \textbf{0.02} & \textbf{0.03} \\ 
                                                                       & $Tr$ & 0.08 & 0.47 & 0.62 & 0.51 & 0.66 & 0.73 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & \textbf{0.00} & \textbf{0.02} & \textbf{0.04} & \textbf{0.04} & 0.05 & 0.06 \\ 
                                                                       & $Tr$ & 0.21 & 0.45 & 0.64 & 0.57 & 0.74 & 0.79 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.73 & 0.73 & 0.76 & 0.81 & 0.86 \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & 0.93 & 0.94 & \textbf{0.96} & \textbf{0.99} \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

\begin{table}[ht]
\caption{Summary of the median Bhattacharyya Coefficients comparisons between the missing data parameters. Each value corresponds to the median Bhattacharyya Coefficient between the Normalised metrics (Robinson-Foulds - RF; Triplets - Tr) between the ``best'' and the ``missing data'' trees (as outlined in Figure 2 in the main text) for the the trees with: Missing Living taxa only ($M_L$); Missing Fossil data only ($M_F$); Number of characters only ($N_C$); and the combination of the three parameters (combined).} 
\begin{tabular}{llcccc}  
  \hline
 Method & Metric & $M_L$ & $M_F$ & $N_C$ & combined \\ 
  \hline
Maximum Likelihood & RF & 0.54 & 0.37 & 0.56 & 0.54 \\ 
                   & Tr & 0.80 & 0.75 & 0.80 & 0.79 \\ 
Bayesian consensus & RF & 0.73 & 0.59 & 0.60 & 0.79 \\ 
   & Tr & 0.86 & 0.67 & 0.81 & 0.81 \\ 
Maximum Likelihood bootstraps & RF & \textbf{0.98} & \textbf{0.96} & \textbf{0.97} & 0.78 \\ 
   & Tr & \textbf{0.99} & \textbf{1.00} & \textbf{1.00} & \textbf{0.96} \\ 
Bayesian posterior trees & RF & 0.86 & 0.93 & 0.94 & 0.68 \\ 
  & Tr & \textbf{0.98} & \textbf{0.99} & \textbf{0.99} & 0.91 \\ 
 \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Summary of the median Bhattacharyya Coefficients comparisons between the missing data parameters and the methods. Each value corresponds to the median Bhattacharyya Coefficient between the Normalised metrics (Robinson-Foulds - RF; Triplets - Tr) between the `methods (as outlined in Figure 3 in the main text) for the the trees with: Missing Living taxa only ($M_L$); Missing Fossil data only ($M_F$); Number of characters only ($N_C$); and the combination of the three parameters (combined).}
\begin{tabular}{llcccc}  
  \hline
 Method & Metric & $M_L$ & $M_F$ & $N_C$ & combined \\ 
  \hline
Maximum likelihood vs. Bayesian consensus & RF & 0.69 & 0.48 & 0.66 & 0.10 \\ 
   & Tr & 0.84 & 0.75 & 0.80 & 0.61 \\ 
Maximum likelihood vs. Bootstraps & RF & 0.29 & 0.32 & 0.21 & 0.69 \\ 
   & Tr & 0.53 & 0.40 & 0.39 & 0.65 \\ 
Maximum likelihood vs. Bayesian posterior trees & RF & 0.61 & 0.71 & 0.47 & 0.80 \\ 
  & Tr & 0.70 & 0.62 & 0.59 & 0.73 \\ 
Bayesian consensus vs. Bootstraps & RF & \textbf{0.02} & \textbf{0.01} & \textbf{0.01} & \textbf{0.00} \\ 
  & Tr & 0.78 & 0.54 & 0.62 & 0.59 \\ 
Bayesian consensus vs. Bayesian posterior trees & RF & \textbf{0.02} & \textbf{0.02} & \textbf{0.04} & \textbf{0.01} \\ 
   & Tr & 0.75 & 0.66 & 0.64 & 0.56 \\ 
Boostraps vs. Bayesian posterior trees & RF & 0.85 & 0.72 & 0.73 & 0.85 \\ 
   & Tr & \textbf{0.96} & 0.91 & 0.93 & \textbf{0.98} \\ 
 \hline
\end{tabular}
\end{table}
%END
\end{document}
